---
title: "Test IRR"
author: "JungHwan Yang"
date: "December 11, 2014"
output: html_document
---

This script is for testing inter-rater reliability (IRR) of the 300 randomly selected tweets about *Obamacare*.

The first 150 tweets were coded by two people.
The other 150 tweets were coded by three people.
(on the day of December 11, 2014)

```{r read data}
path <- "data//random300-coded.csv"
d.coded <- read.csv (path)
```

Since the .csv file contains two different sets of coding for two variables, I make different data frame from the original data.

```{r, echo=FALSE}
d.first.v1 <- d.coded[2:151, c(3, 8)]
names(d.first.v1) <- c("v1.kristen", "v1.jinha")
d.first.v2 <- d.coded[2:151, c(5, 10)]
names(d.first.v2) <- c("v2.kristen", "v2.jinha")
d.last.v1 <- d.coded[151:301, c(13, 18, 23)]
names(d.last.v1) <- c("v1.j", "v1.yini", "v1.rachel")
d.last.v2 <- d.coded[151:301, c(15, 20, 25)]
names(d.last.v2) <- c("v2.j", "v2.yini", "v2.rachel")
```

Test IRR see [This link](http://www.cookbook-r.com/Statistical_analysis/Inter-rater_reliability/)

```{r install "irr" package}
#install.packages("irr")
library(irr)
```

Since it's categorical data for two raters, I calculate Cohen's Kappa for two coders.
In this case, for the first 150 tweets.

```{r}
kappa2(d.first.v1, "unweighted")
kappa2(d.first.v2, "unweighted")
```

Since it's categorical data for three raters, I calculate Fleiss's Kappa for N coders.
In this case, for the last 150 tweets.

```{r}
kappam.fleiss(d.last.v1)
kappam.fleiss(d.last.v2)

# Testing IRR two out of three coders
#kappa2(d.last.v1[ ,1:2], "unweighted")
#kappa2(d.last.v1[ ,c(1,3)], "unweighted")
#kappa2(d.last.v1[ ,2:3], "unweighted")
#kappa2(d.last.v2[ ,1:2], "unweighted")
#kappa2(d.last.v2[ ,c(1,3)], "unweighted")
#kappa2(d.last.v2[ ,2:3], "unweighted")
```

Test with Krippendorff's alpha

- This funciton is tricky because:
    - Need to change a data.frame to a matrix
    - Need to transpose a matrix: t()

```{r}
kripp.alpha(t(as.matrix(d.first.v1[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.first.v2[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.last.v1[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.last.v2[,])), method = "nominal")
```

#### Here, I tried to merge 'unknown (U)' and 'neutral (N)' together

(I could leave out 'unreleveant' tweets and run the same test again.)

```{r recode U and N into U}
d.recoded <- d.coded
d.recoded[d.recoded == 'N'] <- 'U'
```

And repeat the same procedure

```{r, echo=FALSE}
# Make separate dfs
d.re.first.v1 <- d.recoded[2:151, c(3, 8)]
names(d.re.first.v1) <- c("v1.kristen", "v1.jinha")
d.re.first.v2 <- d.recoded[2:151, c(5, 10)]
names(d.re.first.v2) <- c("v2.kristen", "v2.jinha")
d.re.last.v1 <- d.recoded[151:301, c(13, 18, 23)]
names(d.re.last.v1) <- c("v1.j", "v1.yini", "v1.rachel")
d.re.last.v2 <- d.recoded[151:301, c(15, 20, 25)]
names(d.re.last.v2) <- c("v2.j", "v2.yini", "v2.rachel")

# Cohen's kappa
kappa2(d.re.first.v1, "unweighted")
kappa2(d.re.first.v2, "unweighted")

# Fleiss's kappa
kappam.fleiss(d.re.last.v1)
kappam.fleiss(d.re.last.v2)

# Krippendorff's alpha
kripp.alpha(t(as.matrix(d.re.first.v1[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.re.first.v2[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.re.last.v1[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.re.last.v2[,])), method = "nominal")
```
