---
title: "Test IRR 1000 Random Tweets"
author: "JungHwan Yang"
date: "February 17, 2015"
output: html_document
---

This script is for testing inter-rater reliability (IRR) of the 1000 randomly selected tweets about *Obamacare*.

### February 17, 2015

The first 350 tweets were coded by Kristen Bialik (KB) and Ben Sayre (BS).
The second 350 tweets were coded by Jeff Tischauser (JT) and Yini Zhang (YZ).
The third 300 tweets were coded by JungHwan Yang (JY) and Rachel Kornfield (RK).


```{r read data, eval = F}
###############################################################################
path <- "../R Project//Data/random1000-coded/random1000-mergedCoding.csv"
d.coded <- read.csv (path)
###############################################################################
```



Since the .csv file contains three different sets of coding for the variable (e.g., user ideology), I make different data frame from the original data.

```{r}
###############################################################################
d.1.350 <- d.coded[1:350, c(2, 3)] # 1-350
#names(d.1.350) <- c("KB", "BS")
d.2.350 <- d.coded[1:350, c(5, 6)] # 351-700
d.3.300 <- d.coded[1:300, c(9, 10)] # 701-1000
###############################################################################
```

Test IRR see [This link](http://www.cookbook-r.com/Statistical_analysis/Inter-rater_reliability/)

```{r install "irr" package}
###############################################################################
#install.packages("irr")
library(irr)
###############################################################################
```

### Test with Krippendorff's alpha

This funciton is tricky because:

- Need to change a data.frame to a matrix
- Need to transpose a matrix: t()

```{r}
###############################################################################
# Krippendorff's alpha
kripp.alpha(t(as.matrix(d.1.350[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.2.350[,])), method = "nominal")
kripp.alpha(t(as.matrix(d.3.300[,])), method = "nominal")
###############################################################################
```

### Test with Cohen's Kappa

Since it's categorical data for two raters, I calculate Cohen's Kappa for two coders.

```{r}
###############################################################################
# Cohen's kappa
kappa2(d.1.350, "unweighted")
kappa2(d.2.350, "unweighted")
kappa2(d.3.300, "unweighted")
###############################################################################
```

```{r}
###############################################################################
path.new <- "../R Project//Data/random1000-coded/random1000-mergedCoding.csv"
d.coded.new <- read.csv(path.new)
###############################################################################
```

Here I test IRR among three people for only #351-700 tweets that Jinha coded.

```{r}
###############################################################################
d.2.350.new <- d.coded.new[1:350, c(5, 6, 7)] # 351-700
d.2.350.new.1 <- d.coded.new[1:350, c(5, 6)] # 351-700
d.2.350.new.2 <- d.coded.new[1:350, c(5, 7)] # 351-700
d.2.350.new.3 <- d.coded.new[1:350, c(6, 7)] # 351-700
###############################################################################
```

### Test with Krippendorff's alpha

This funciton is tricky because:

- Need to change a data.frame to a matrix
- Need to transpose a matrix: t()

```{r}
###############################################################################
library(irr)

# Krippendorff's alpha
kripp.alpha(t(as.matrix(d.2.350.new[,])), method = "nominal") #a = .70
kripp.alpha(t(as.matrix(d.2.350.new.1[,])), method = "nominal") #a = .71
kripp.alpha(t(as.matrix(d.2.350.new.2[,])), method = "nominal") #a = .66
kripp.alpha(t(as.matrix(d.2.350.new.3[,])), method = "nominal") #a = .75
###############################################################################
```

```{r read data, eval = F}
###############################################################################
path <- "Data/merged-IRR50-WZ-YW.csv"
d.coded <- read.csv (path, header = T)

path <- "Data/merged-IRR50-JY-YW-RK.csv"
d.coded <- read.csv (path, header = T)

###############################################################################
```


```{r}
library(irr)
# Krippendorff's alpha
kripp.alpha(t(as.matrix(d.coded[1:55,2:3])), method = "nominal")
#WZ-YW: a = .70
#JY-YW: a = .68
kripp.alpha(t(as.matrix(d.coded[1:55,3:4])), method = "nominal")
```

```{r eval = F}
library(knitr); library(pandoc)
knit2html('Scripts/04 irr test 1000.Rmd')
```