---
title: "07 LDA"
author: "JungHwan Yang"
date: "April 10, 2015"
output: html_document
---

### Linear Discriminant Analysis (LDA)

We need to modify data frame before running LDA. Here, I am using a working data frame named training_dtm_desc

To begin with, here's the list of popular keywords of profile description among the conservatives and the librals:

| Conservative | Libaral  |
| -------------: |-------------:|
| conservative/conservatives/conservatism/conservatarian| liberal |
| christian | progressive |
| tea (/party) | democrat |
| freedom | people |
| god | left |
| constitution/constitutional/constitutionalist | social |
| liberty | public |
| republican | feminist |
| libertarian | affordable |
| patriot | prochoice |
| prolife | obamacare |

Since I haven't done stemming, I do here manually.

```{r}
# Stemming
training_dtm_combined$conservative <-
  training_dtm_combined$conservative + training_dtm_combined$conservatives +
  training_dtm_combined$conservatism + training_dtm_combined$conservatarian
training_dtm_combined$conservatives <- NULL
training_dtm_combined$conservatism <- NULL
training_dtm_combined$conservatarian <- NULL

training_dtm_combined$constitution <-
  training_dtm_combined$constitution + training_dtm_combined$constitutional +
  training_dtm_combined$constitutionalist
training_dtm_combined$constitutional <- NULL
training_dtm_combined$constitutionalist <- NULL

training_dtm_combined$tweet <-
  training_dtm_combined$tweet + training_dtm_combined$tweeter +
  training_dtm_combined$tweeting + training_dtm_combined$tweets
training_dtm_combined$tweet <- NULL
training_dtm_combined$tweeter <- NULL
training_dtm_combined$tweeting <- NULL
training_dtm_combined$tweets <- NULL
```

```{r}
# Stemming
training_dtm_combined_sm$conservative <-
  training_dtm_combined_sm$conservative + training_dtm_combined_sm$conservatism +
  training_dtm_combined_sm$conservatarian
training_dtm_combined_sm$conservatism <- NULL
training_dtm_combined_sm$conservatarian <- NULL

training_dtm_combined_sm$constitution <-
  training_dtm_combined_sm$constitution + training_dtm_combined_sm$constitutional
training_dtm_combined_sm$constitutional <- NULL

training_dtm_combined_sm$tweets <-
  training_dtm_combined_sm$tweeter +
  training_dtm_combined_sm$tweeting + training_dtm_combined_sm$tweets
training_dtm_combined_sm$tweeter <- NULL
training_dtm_combined_sm$tweeting <- NULL

```

```{r, echo = F}
library(MASS)
# Linear Discriminant Analysis with Jacknifed Prediction 
# Use profile description
fit.1 <- 
  lda(User_Ideology ~ conservative + christian + tea + #conservative
        freedom + god + constitution + liberty + republican +
        libertarian + patriot + prolife +
        business +
        liberal + progressive + democrat + people + left + #liberal
        social + public + feminist + affordable + prochoice + obamacare +
        proud + truth + policy + activist + working +
        health + twitter + rts + research + place + #unknown
        interested + endorsements + reporter + world, 
        data = training_dtm_combined, 
        na.action="na.omit", CV=TRUE)
fit.1 # show results

# Assess the accuracy of the prediction
# percent correct for each category of User_Ideology
ct <- table(training_dtm_combined$User_Ideology, fit.1$class)
diag(prop.table(ct, 1))
# total percent correct

sum(diag(prop.table(ct)))


ct <- table(test_dtm$User_Ideology, test.result$class)
# Linear Discriminant Analysis with Jacknifed Prediction 
# Use profile description and tweet hashtags
fit.2 <- 
  lda(User_Ideology ~ conservative + christian + tea + #conservative
        freedom + god + constitution + liberty + republican +
        libertarian + patriot + prolife +
        business +
        liberal + progressive + democrat + people + left + #liberal
        social + public + feminist + affordable + prochoice + obamacare +
        proud + truth + policy + activist + working +
        health + twitter + rts + research + place + #unknown
        interested + endorsements + reporter + world +
        h.tcot + h.teaparty + h.gop + h.sgp + h.tlot + h.repeal +
        h.aca + h.p2 + h.hcr + h.obama2012 +
        h.news + h.job + h.jobs +
        h.ilikeobamacare, 
        data = training_dtm_combined,
        na.action="na.omit", CV=TRUE)
fit.2 # show results

# Assess the accuracy of the prediction
# percent correct for each category of User_Ideology
ct <- table(training_dtm_combined$User_Ideology, fit.2$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))

# Linear Discriminant Analysis with Jacknifed Prediction 
# Use profile description and tweet hashtags
fit.3 <- 
  lda(User_Ideology ~ ., 
        data = training_dtm_combined, 
        na.action="na.omit", CV=TRUE, tol = .03)
fit.3 # show results

# Assess the accuracy of the prediction
# percent correct for each category of User_Ideology
ct <- table(training_dtm_combined$User_Ideology, fit.3$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))

```
