---
title: "08 Recode Verified Users"
author: "JungHwan Yang"
date: "May 3, 2016"
output: html_document
---

I found that handcoding randomly selected tweets might miss the tweets from an influential account (e.g., @nytimes). If machine learning algorithm mistakenly classified the influential account, it may cause errors in other accounts' classfication because their information is more likely to be popular among other Twitter users.

So, I picked verified users (who are more likely to be influentials) from the dataset and picked the top *1.5%* (double check) non-verified users and recoded their ideology with the other coder (Rachel Kornfield). We coded the all verified accounts and a number of non-verified accounts that have clear political leaning.

```{r}
setwd('/Users/JYang/Documents/SMAD/smad-methods/Obamacare/R Project/Data/')
d <- read.csv('elite recoded data/List of Obamacare Elites - verified.csv')
```

The script below describes how I merged the new coding with the old coding.

```{r}
d$Ideology.recode <- 
  ifelse((as.character(d$Ideology) == as.character(d$Ideology.recode) |
          as.character(d$Ideology.recode) == ""),
         as.character(d$Ideology),
         as.character(d$Ideology.recode))
d$Ideology <- d$Ideology.recode
```

So, now I have recoded classification of the verified users.
Now, merge with 1643 coded file using merge() - similar to VLOOKUP in Excel.

http://www.rforexcelusers.com/vlookup-in-r/

```{r}
# Read user names from the formerly handcoded data
d.1643 <- read.csv('FinalHandcoded1643.csv')

# # Since the variable names of the two file don't match, I'll change it here.
# names(d)[c(5,8)] <- c("screen_name", "User_Ideology")

# Merge two dataframes
d.extra <- 
  merge(d.1643, d[, c("Username", "Ideology")],
        by.x = "screen_name", by.y = "Username", all = T)

# Merge Idelogy coding
temp <- 
  ifelse(as.character(d.extra$User_Ideology) == as.character(d.extra$Ideology) |
         is.na(d.extra$Ideology),
         as.character(d.extra$User_Ideology), as.character(d.extra$Ideology))
d.extra$User_Ideology <- 
  ifelse(is.na(temp), as.character(d.extra$Ideology),
         temp)
d.extra$Ideology <- NULL
rm(temp)
```

Now, the new coding is merged with the old coding. Now, I collected data

```{r}
# These are the elite users who we additionally coded and that were not in the initial coding set.
# write.csv (d.extra[1644:nrow(d.extra),1], "extraEliteUsersList.csv",
#            row.names = F, quote = F)
# Here I pull radom sample of their tweets from *.RData file that I made using obamacare sample json.json
# library(rjson)
# con <- file("obamacare sample json.json",open = "r")
# obamacare<-vector("list")
# i=0
# while(T){
#   i<-i+1
#   temp<-readLines(con,1)
#   if(length(temp)==0){
#     print("reach the end")
#     break
#   } else temp<-sub('.*\\t', '',temp, perl = TRUE)#get rid of the series ahead of json format
#   obamacare[[i]]<-fromJSON(temp)
# }
# close(con)
# 
# rm(con); rm(i); rm(temp)
# save(obamacare,file="../R Project/Data/obamacare.RData")
load("~/Documents/SMAD/smad-methods/Obamacare/R Project/Data/obamacare.RData")

# using 'obamacare' object, which contains raw json data, I extracted these properties:
screen_name <- sapply(obamacare, with, user$screen_name)
text <- sapply(obamacare, with, text)
retweet_count <- sapply(obamacare, with, retweet_count)
id_str <- sapply(obamacare, with, id_str)
created_at <- sapply(obamacare, with, id_str)
verified <- sapply(obamacare, with, user$verified)
user_id_str <- sapply(obamacare, with, user$id_str)
statuses_count <- sapply(obamacare, with, user$statuses_count)
followers_count <- sapply(obamacare, with, user$followers_count)
name <- sapply(obamacare, with, user$name)
friends_count <- sapply(obamacare, with, user$friends_count)
# some elements require to do as follows to handle a list
description <-
  sapply(obamacare, function(x) return(x$user$description))
description <- 
  sapply(description, function(x) ifelse(is.null(x), NA, x)) # list to vector
time_zone <-
  sapply(obamacare, function(x) return(x$user$time_zone))
time_zone <- 
  sapply(time_zone, function(x) ifelse(is.null(x), NA, x))
# retweet_user <- 
#   sapply(obamacare, function(x) return(x$retweeted_status$user$screen_name))
# retweet_user <- 
#   sapply(retweet_user, function(x) ifelse(is.null(x), NA, x))

# get_re = function(x) return (x$retweeted_status$user$screen_name)
# retweet_user = sapply(obamacare, FUN = get_re)


d.all <-
  data.frame(screen_name, text, retweet_count, id_str, created_at, verified,
             user_id_str, description, followers_count, name, time_zone,
             friends_count)
rm(screen_name); rm(text); rm(retweet_count); rm(id_str); rm(created_at);
rm(verified); rm(user_id_str); rm(description); rm(followers_count);rm(name);
rm(time_zone); rm(friends_count)

# get_re = function(x) return (x$retweeted_status$user$screen_name)
# retweet_user = sapply(obamacare, FUN = get_re)

d.all$retweet_user <- NULL

# Find the verified users (d.extra) from d.all
## Make a list of additional users
extra.list <- as.vector(d.extra[1644:nrow(d.extra), c(1, 3)])
## Find the tweets from the additional users from d.all
temp <- d.all[d.all$screen_name %in% extra.list$screen_name, ]
## Find one tweet per user
temp <- subset(temp, !duplicated(screen_name)) 
## Merge Ideology coding of extra.list (info from d.extra) and temp
temp <- merge(temp, extra.list, by.all = "screen_name", all = T)
## Merge as d.extra
d.extra <-
  merge(d.1643[,], temp, by.all = "screen_name", all = T)

## Export d.extra as d.2182.csv
write.csv (d.extra, "d.2182.csv", row.names = F, quote = T)

rm(temp)
```
